Maximum Allowable Current Determination of RBS By Using a Directed Graph Model and Greedy Algorithm

### 2023-09-12 paper/SST/review_response.tex

\documentclass[12pt,american]{scrartcl}
\usepackage{babel}
\usepackage[babel]{microtype}
\usepackage[babel]{csquotes}

\usepackage[journal={Space: Science \& Technology},
			manuscript={SPACE-D-23-00082},
			editor={Dr. Tian}]{reviewresponse}

\usepackage[T1]{fontenc}
\usepackage{lmodern}
%\usepackage{newcent}
%\usepackage[scaled]{beramono}

\usepackage[]{biblatex}
\bibliography{2-SST_review.bib}

\usepackage{hyperref}

\title{Maximum Allowable Current Determination of RBS By Using a Directed Graph Model and Greedy Algorithm}
\author{Dr. Cheng Qian, on behalf of all authors}

\begin{document}
\maketitle

% Cover Letter
\include{2-SST_cover_letter}

% Reviewer 1
\reviewer
% Comment 1
\begin{revcomment}
	The authors should explain the most important achievements of the proposed method quantitatively, in the abstract.
\end{revcomment}
\begin{revresponse}
	We appreciate the reviewer's valuable feedback and have carefully considered their suggestion. In response, we have re-written the relevant content in the abstract to provide a quantitative analysis of the most important achievements of our proposed method.

	The revised abstract now highlights that our method not only achieves the same results as the traversal method but also demonstrates significantly improved computational efficiency. Specifically, our method achieves computational efficiency improvements ranging from 3000 to 75000 times, primarily depending on the number of switches involved. This enhancement in computational efficiency is a key advantage of our method.

	Furthermore, our method stands out for its ability to accurately calculate the MAC of RBSs with arbitrary configurations, even in scenarios with random isolated batteries. This capability expands the applicability of our method to a wider range of scenarios and enhances its practical utility.

	We believe that these quantitative achievements, as described in the revised abstract, effectively demonstrate the effectiveness and superiority of our proposed method.
\end{revresponse}

% Comment 2
\begin{revcomment}
	The literature review in the introduction section is very short, and the related works, especially the works published in recent years, have not been well reviewed and compared, and the conclusions about the existing research gaps have not been presented.
\end{revcomment}
\begin{revresponse}

\end{revresponse}

% Comment 3
\begin{revcomment}
	It is necessary for the authors to clearly state research contribution and achievements as bullet points at the end of the Introduction section.
\end{revcomment}
\begin{revresponse}

\end{revresponse}

% Comment 4
\begin{revcomment}
	The authors need to present the complexity of their proposed method and compare it with some other state-of-the-art or successful classic methods.
\end{revcomment}
\begin{revresponse}

\end{revresponse}

% Comment 5
\begin{revcomment}
	The authors don't discuss the limitations of the study correctly.
\end{revcomment}
\begin{revresponse}

\end{revresponse}

% Comment 6
\begin{revcomment}
	Some typos should be double check.
\end{revcomment}
\begin{revresponse}

\end{revresponse}

% Comment 7
\begin{revcomment}
	The author should explain more why solution quality of their proposed approach is much better than the others?
\end{revcomment}
\begin{revresponse}

\end{revresponse}

% Comment 8
\begin{revcomment}
	Authors should mention some novel works in the field in the introduction, specially refer to this 2023 reference: An efficient lightweight algorithm for scheduling tasks onto dynamically reconfigurable hardware using graph-oriented simulated annealing, which uses graph-based method. Mention and refer to it in the introduction section.
\end{revcomment}
\begin{revresponse}

\end{revresponse}

% Comment 9
\begin{revcomment}
	Authors need to explain about the accuracy, sufficiency and reliability of their results? How do they verify and validate the results?
\end{revcomment}
\begin{revresponse}

\end{revresponse}

% \begin{revcomment}
% 	Everything else is really good.
% \end{revcomment}
% \begin{revresponse}
% 	We totally agree. We also added the following to the new version of the manuscript
% 	\begin{changes}
% 		This really important sentence was added to the paper.
% 	\end{changes}
% \end{revresponse}

\end{document}

### 2023-09-13 paper/SST/SST_main.tex
完成了 Xu 的意见修改 (v1.4)

% 【done】 
% =====0909
% 按 Q 修改意见修改 0901 【优先】
% =====0910
% 1. 摘要修改，量化我们的成果：explain the most important achievements of the proposed method quantitatively
% 2. 介绍修改，相关文献：
%   2.1 RBS 结构分析相关的
%   2.2 网络流（最大流）相关（但因为问题不同，无法使用，提一句穷举）
% 3. 介绍修改，逐点列出我们的贡献：state research contribution and achievements as bullet points at the end of the Introduction section
% 4. 讨论修改，增加算法复杂度，以及和穷举法的比较（该领域尚为空白，没有sota的算法）
% 5. 讨论修改，增加算法的 limitations（根据复杂度，大规模不好用）
% 6. 讨论修改，增加结果的准确性介绍（和穷举结果比较）：explain about the accuracy, sufficiency and reliability of their results? How do they verify and validate the results
% 7. 修改算法的第15步
% 8. 重写总结
% 9. 添加文献
% =====0911
% 1. introduction 整体逻辑不流畅，跳跃过大
% 2. introduction 文献
% 2. conclusion 结尾，可以加上一两句说说这个方法的应用价值之类的，吹一吹
% 3. abstract
%   3.1 删去 75000 倍的效率；
%   3.2 凝练一点，就是说这个方法把遍历法中的枚举开关状态组合，转换为了对最短路径的组合；
%   3.3 算法复杂度、效率提升倍数=2^开关数/2^电池数
%   3.4 调整 discussion 的相关内容
% 4. 删去 最大流
% 5. 按 Q 的意见修改

@@

\usepackage[defaultcolor=red]{changes}
% \added{xxx}
% \deleted{xxxx}
% \replaced{a}{b} 原文的b替换成a
% \usepackage[final]{changes}
% \usepackage{easyReview} % texstudio 部分

%%%%%% Bibliography %%%%%%
% Replace "sample" in the \addbibresource line below with the name of your .bib file.
% \usepackage[style=nejm, citestyle=numeric-comp, sorting=none]{biblatex}
% \addbibresource{SST_main.bib}

@@

\added{
Recently, the flexibility and reconfigurability of RBS have been utilized to design various structures in order to meet application requirements and improve system performances. 
Ci et al. \cite{ci2007novel} proposed a RBS structure that can dynamically adjust the batteries discharge rate to fully exploit the available capacity of each battery. 
Jan's \cite{9209774,engelhardt2021double} structures had the ability to reconfigure structures with variant batteries in series to reach the voltage requirements during electric vehicle charging, which constantly change.
The structure proposed by Visairo et al.\cite{visairoReconfigurableBatteryPack2008}, as shown in Figure \ref{fig:stru-Visairo}, can change the system's output voltage based on load conditions, thereby reducing the power loss of the voltage regulator during the power supply process and improving energy utilization efficiency. 
For the same purpose to enhance the energy efficiency of the system, Lawson et al. \cite{lawsonSoftwareConfigurableBattery2012} and He et al. \cite{he2014reconfiguration} also proposed simplified structures which has less switches than Visairo's design.
Kim et al. \cite{kim2009dynamic} improved the system's ability to recover from battery failures by introducing multiple ports to the structure. 
The design of these structures mainly relies on the experience of researchers and lacks rigorous structural analysis methods and quantitative evaluation criteria. 
This may result in suboptimal structures, inability to fully leverage the performance advantages of RBS, and even potential safety hazards that prevent practical applications of RBS. 
To tackle these issues, several approaches to analyze the RBS structure and performance have been proposed in the literature.
For instance, Chen et al.\cite{chenSneakCircuitTheory2021} proposed a systematic approach based on the sneak circuit theory to fundamentally avoid the short-circuit problem of reconfigurable battery systems. 
They thoroughly analyzes all paths between the cathode and anode of each battery in the RBS and identifies paths that only contain switches as short-circuit paths for pre-checking before system reconfiguration. 
Han et al.\cite{han2021analysis} derived an analytical expression for the maximum switch current during battery system reconfiguration for a specific RBS structure. 
This helps guide the selection of switches and provide support for the hardware design of RBS.
}

\added{
The battery has an appropriate range of operating currents, and excessive current can lead to a decrease and degradation in battery performance, or even damage\cite{lotfi2017li}.
likewise, for RBS composed of finite batteries, there is also an upper limit on the system's output current, known as the maximum allowable current (MAC). 
Exceeding this threshold can result in current overload on certain batteries of the system. 
Unfortunately, few studies on the RBS structure analysis have been conducted to determine the MAC of RBSs.
A intuitive and straightforward method is to enumerate all possible switch states and calculate the output current of the system under each reconfigurated structure.
But this method is inefficient and time-consuming, especially for RBSs with a large number of switches.
}

@@

\added{
To effectively solve the switches states of MAC while strongly decreasing the unnecessary reconfigured structures to compute, and still robust in the scenarios with battery isolation, the greedy algorithm is adopted and adapted to solve the MAC problem in this paper.
Meanwhile, an improved direct graph model, considering the voltage, internal resistance, and maximum allowable current of the battery, and the external load, is porposed and emploied to obtain the accuracy value of MAC.
The correctness and effectiveness of the method in this paper are verified by two published 4-battery-RBSs and one with more complex structure.
}
\deleted{In this study, a directed graph model and greedy algorithm are employed to determine the MAC of RBS and the corresponding control strategy, effectively calculating the MAC for RBSs with arbitrary structures, including scenarios with isolated batteries.}
\added{The main contributions of the paper can be summarized as follows:}
\begin{itemize}
  \item \added{Proposing a effective method to determine the MAC of RBSs with arbitrary structures, including scenarios with isolated batteries, for the first time.}
  \item \added{Application of the greedy algorithm to solve the MAC problem, whose computational complexity is greatly reduced compared with the brute force algorithm.}
  \item \added{introducing an improved directed graph model, considering the voltage, internal resistance, and maximum allowable current of the battery, and the external load, to achieve the current analysis of the RBS.}
\end{itemize}

@@

\added{
From the literature research we have conducted, no formal report on the algorithm for MAC in RBS has been found yet.
The brute force algorithm, which goes through all possible switch states, is the most straightforward way to solve the MAC problem and is used as a benchmark for the proposed greedy algorithm.
Assuming that a RBS has $N_b$ batteries and $N_s$ switches, and the corresponding directed graph has $N$ nodes, it requires $2^{N_s}$ iterations to traverse all reconfigured structures.
The calculation for each reconfigured structure by Equations \ref{eq:I_o}-\ref{eq:eta} requires matrix inversion and matrix multiplication, with a time complexity of $O(N^3+2N^2N_b+N^2N_s+NN^2_b)$.
Therefore, the time complexity of the brute force algorithm is $O(2^{N_s}(N^3+2N^2N_b+N^2N_s+NN^2_b))$.
The greedy algorithm proposed in this paper requires find the $SP$ for each battery, which requires $N_b$ iterations.
Each $SP$ can be obtained by couple Dijkstra algorithms.
Therefore, the total time complexity of calculating all $SP$s is $O(2N_b(N_b+2N_s)\log N)$.
According to the Appendix \ref{alg:greedy}, the RBS can reconfigure $C^{N_{set}}_{N_b}$ structures by selecting $N_{set}$ batteries from $N_b$ batteries, which is $\sum^{N_b}_{N_{set}=1}C^{N_{set}}_{N_b}/N_b \approx 2^{N_b}/N_b$ on average.
Hence, with bisection method, the time complexity of the greedy algorithm is $O(2^{N_b}/N_b(N^3+2N^2N_b+N^2N_s+NN^2_b)\log N_b+2N_b(N_b+2N_s)\log N)$, i.e., $O(2^{N_b}/N_b(N^3+2N^2N_b+N^2N_s+NN^2_b)\log N_b)$.
Based on currently proposed RBS structures\cite{ciNovelDesignAdaptive2007,alahmadBatterySwitchArray2008,kimDependableEfficientScalable2010b,kimBalancedReconfigurationStorage2011a,taesickimSeriesconnectedSelfreconfigurableMulticell2012a,6843711}, the number of batteries $N_b$, switches $N_s$, and nodes $N$ have the following quantitative relationships: $N_s \approx (3\sim 5)N_b$, $N \approx N_s$. 
After simplifying, the time complexity of the greedy algorithm is $O(2^{N_b}N_s^2\log N_b)$, while it is $O(2^{N_s}N_s^3)$ for brute force algorithm.
Therefore, it is reasonable to believe that as the size of the RBS increases, especially the number of the swithes, the greedy algorithm will have an advantage over the algorithm that goes through all reconfigured structures.
This can be comfirmed from the number of structures required for MAC determination in the previous subsection. 
Compared to the brute force algorithm, the efficiency of the method based on the greedy algorithm has been improved by 3000 to 75000 times, which is theoretically $N_s 2^{N_s - N_b} \log N_b$ times according to the above time complexity analysis.
Among the three RBS structures, the highest is the RBS structure with 19 switches (Figure \ref{fig:study-stru-my}).
This benefit from two key points:
(1) The $SP$s guide the RBS to reconfigure reasonable structures, rather than blindly going through all possible structures. This reduces the factor in complexity from $2^{N_s}$ to $2^{N_b}$, which is the main reason for the improvement in efficiency;
(2) The bisection method further accelerates this process.
However, the greedy algorithm proposed in this paper still contains exponential terms in the time complexity, which means it may not be able to handle extremely large-scale RBS structures.
}

@@

This paper proposes a pervasive and automatical method for computing the MAC of \replaced{a}{the} given RBS.
\added{
The method is implemented by a greedy algorithm combined with a directed graph model which considers the voltage, internal resistance, and maximum allowable current of the batteries, as well as the external load.
The main advantage of this method is its ability to calculate the MAC of RBSs with arbitrary structures.
Even in the scenarios with random isolated batteries, the method remains effective.
Compared with the brute force algorithm, the proposed method has higher computational efficiency under the same calculation results.
This is achieved by two key points when constructing the greedy algorithm: 
(1) Calculate the shortest path of each battery by Dijkstra algorithm to obtain the $SP$ of each battery; 
(2) determine the maximum number of available batteries by bisection method to reduce the computational complexity.
This method helps to fully tap the current output potential of the RBS, guide the RBS structure design and optimization in the design stage, and assist in evaluating the current overload risk of the system in practical applications.
}
\deleted{The method is implemented by a greedy algorithm combined with a directed graph model , whose effectiveness is tested on a novel and complex RBS structure.
The method remains effective for the application scenario of RBS battery isolation and demonstrates that the novel structure has the advantage on flexible output current and convenient battery isolation.
Future research could focus on developing new indictors to evaluate the performance of the RBS with the currents and voltages obtained by the method, as well as modifying the equivalent model of the battery to allow for more accurate simulations of the RBS, including transient analysis.}

@@

This work does not require any data to be declared or publicly disclosed.
\begin{thebibliography}{10}

\bibitem{alahmadBatterySwitchArray2008}
Mahmoud Alahmad, Herb Hess, Mohammad Mojarradi, William West, and Jay Whitacre.
\newblock Battery switch array system with application for {{JPL}}'s
  rechargeable micro-scale batteries.
\newblock {\em Journal of Power Sources}, 177(2):566--578, March 2008.

\bibitem{chenSneakCircuitTheory2021}
Si-Zhe Chen, Yule Wang, Guidong Zhang, Le~Chang, and Yun Zhang.
\newblock Sneak {{Circuit Theory Based Approach}} to {{Avoiding Short-Circuit
  Paths}} in {{Reconfigurable Battery Systems}}.
\newblock 68(12):12353--12363, 2021.

\bibitem{choCommercialResearchBattery2015}
Jaephil Cho, Sookyung Jeong, and Youngsik Kim.
\newblock Commercial and research battery technologies for electrical energy
  storage applications.
\newblock {\em Progress in Energy and Combustion Science}, 48:84--101, June
  2015.

\bibitem{ci2007novel}
Song Ci, Jiucai Zhang, Hamid Sharif, and Mahmoud Alahmad.
\newblock A novel design of adaptive reconfigurable multicell battery for
  power-aware embedded networked sensing systems.
\newblock In {\em IEEE GLOBECOM 2007-IEEE Global Telecommunications
  Conference}, pages 1043--1047. IEEE, 2007.

\bibitem{ciNovelDesignAdaptive2007}
Song Ci, Jiucai Zhang, Hamid Sharif, and Mahmoud Alahmad.
\newblock A {{Novel Design}} of {{Adaptive Reconfigurable Multicell Battery}}
  for {{Power-Aware Embedded Networked Sensing Systems}}.
\newblock In {\em {{IEEE GLOBECOM}} 2007-2007 {{IEEE Global Telecommunications
  Conference}}}, pages 1043--1047, November 2007.

\bibitem{desiqueiraControlStrategySmooth2021}
Luanna Maria~Silva {de Siqueira} and Wei Peng.
\newblock Control strategy to smooth wind power output using battery energy
  storage system: {{A}} review.
\newblock {\em Journal of Energy Storage}, 35:102252, March 2021.

\bibitem{10.1145/321694.321699}
Jack Edmonds and Richard~M. Karp.
\newblock Theoretical improvements in algorithmic efficiency for network flow
  problems.
\newblock {\em J. ACM}, 19(2):248–264, apr 1972.

\bibitem{9209774}
Jan Engelhardt, Tatiana Gabderakhmanova, Gunnar Rohde, and Mattia Marinelli.
\newblock Reconfigurable stationary battery with adaptive cell switching for
  electric vehicle fast-charging.
\newblock In {\em 2020 55th International Universities Power Engineering
  Conference (UPEC)}, pages 1--6, 2020.

\bibitem{engelhardt2021double}
Jan Engelhardt, Jan~Martin Zepter, Tatiana Gabderakhmanova, Gunnar Rohde, and
  Mattia Marinelli.
\newblock Double-string battery system with reconfigurable cell topology
  operated as a fast charging station for electric vehicles.
\newblock {\em Energies}, 14(9):2414, 2021.

\bibitem{doi:10.1137/0204043}
Shimon Even and R.~Endre Tarjan.
\newblock Network flow and testing graph connectivity.
\newblock {\em SIAM Journal on Computing}, 4(4):507--518, 1975.

\bibitem{fengPropagationMechanismsDiagnosis2019}
Fei Feng, Xiaosong Hu, Lin Hu, Fengling Hu, Yang Li, and Lei Zhang.
\newblock Propagation mechanisms and diagnosis of parameter inconsistency
  within {{Li-Ion}} battery packs.
\newblock {\em Renewable and Sustainable Energy Reviews}, 112:102--113,
  September 2019.

\bibitem{han2021analysis}
Weiji Han, Anton Kersten, Changfu Zou, Torsten Wik, Xiaoliang Huang, and
  Guangzhong Dong.
\newblock Analysis and estimation of the maximum switch current during battery
  system reconfiguration.
\newblock {\em IEEE Transactions on Industrial Electronics}, 69(6):5931--5941,
  2021.

\bibitem{hanNextGenerationBatteryManagement2020a}
Weiji Han, Torsten Wik, Anton Kersten, Guangzhong Dong, and Changfu Zou.
\newblock Next-{{Generation Battery Management Systems}}: {{Dynamic
  Reconfiguration}}.
\newblock {\em IEEE Industrial Electronics Magazine}, 14(4):20--31, December
  2020.

\bibitem{hongwenheStateofChargeEstimationLithiumIon2011}
Hongwen He, Rui Xiong, Xiaowei Zhang, Fengchun Sun, and JinXin Fan.
\newblock State-of-{{Charge Estimation}} of the {{Lithium-Ion Battery Using}}
  an {{Adaptive Extended Kalman Filter Based}} on an {{Improved Thevenin
  Model}}.
\newblock {\em IEEE Transactions on Vehicular Technology}, 60(4):1461--1469,
  May 2011.

\bibitem{heExploringAdaptiveReconfiguration2013}
Liang He, Lipeng Gu, Linghe Kong, Yu~Gu, Cong Liu, and Tian He.
\newblock Exploring {{Adaptive Reconfiguration}} to {{Optimize Energy
  Efficiency}} in {{Large-Scale Battery Systems}}.
\newblock In {\em 2013 {{IEEE}} 34th {{Real-Time Systems Symposium}}}, pages
  118--127, December 2013.

\bibitem{he2014reconfiguration}
Liang He, Linghe Kong, Siyu Lin, Shaodong Ying, Yu~Gu, Tian He, and Cong Liu.
\newblock Reconfiguration-assisted charging in large-scale lithium-ion battery
  systems.
\newblock In {\em 2014 ACM/IEEE International Conference on Cyber-Physical
  Systems (ICCPS)}, pages 60--71. IEEE, 2014.

\bibitem{6843711}
Liang He, Linghe Kong, Siyu Lin, Shaodong Ying, Yu~Gu, Tian He, and Cong Liu.
\newblock Reconfiguration-assisted charging in large-scale {{Lithium-ion}}
  battery systems.
\newblock In {\em 2014 {{ACM}}/{{IEEE International Conference}} on
  {{Cyber-Physical Systems}} ({{ICCPS}})}, pages 60--71, April 2014.

\bibitem{jeevarajanBatterySafetyQualifications2012}
J.~A. Jeevarajan and C.~Winchester.
\newblock Battery {{Safety Qualifications}} for {{Human Ratings}}.
\newblock {\em Interface magazine}, 21(2):51--55, January 2012.

\bibitem{kim2009dynamic}
Hahnsang Kim and Kang~G Shin.
\newblock On dynamic reconfiguration of a large-scale battery system.
\newblock In {\em 2009 15th IEEE Real-Time and Embedded Technology and
  Applications Symposium}, pages 87--96. IEEE, 2009.

\bibitem{kimDependableEfficientScalable2010b}
Hahnsang Kim and Kang~G. Shin.
\newblock Dependable, efficient, scalable architecture for management of
  large-scale batteries.
\newblock In {\em Proceedings of the 1st {{ACM}}/{{IEEE International
  Conference}} on {{Cyber-Physical Systems}}}, {{ICCPS}} '10, pages 178--187,
  {New York, NY, USA}, April 2010. {Association for Computing Machinery}.

\bibitem{taesickimSeriesconnectedSelfreconfigurableMulticell2012a}
Taesic Kim, Wei Qiao, and Liyan Qu.
\newblock A series-connected self-reconfigurable multicell battery capable of
  safe and effective charging/discharging and balancing operations.
\newblock In {\em 2012 {{Twenty-Seventh Annual IEEE Applied Power Electronics
  Conference}} and {{Exposition}} ({{APEC}})}, pages 2259--2264, February 2012.

\bibitem{kimBalancedReconfigurationStorage2011a}
Younghyun Kim, Sangyoung Park, Yanzhi Wang, Qing Xie, Naehyuck Chang, Massimo
  Poncino, and Massoud Pedram.
\newblock Balanced reconfiguration of storage banks in a hybrid electrical
  energy storage system.
\newblock In {\em 2011 {{IEEE}}/{{ACM International Conference}} on
  {{Computer-Aided Design}} ({{ICCAD}})}, pages 624--631, November 2011.

\bibitem{lawsonSoftwareConfigurableBattery2012}
Barrie Lawson.
\newblock A {{Software Configurable Battery}}.
\newblock {\em EVS26 International Battery, Hybrid and Fuel Cell Electric
  Vehicle Symposium}, 2012.

\bibitem{lotfi2017li}
Nima Lotfi, Jie Li, Robert~G Landers, and Jonghyun Park.
\newblock Li-ion battery state of health estimation based on an improved single
  particle model.
\newblock In {\em 2017 American Control Conference (ACC)}, pages 86--91. IEEE,
  2017.

\bibitem{mousavig.VariousBatteryModels2014}
S.M. Mousavi~G. and M.~Nikdel.
\newblock Various battery models for various simulation studies and
  applications.
\newblock {\em Renewable and Sustainable Energy Reviews}, 32:477--485, April
  2014.

\bibitem{pomboHybridPowerSystem2021}
Daniel~V{\'a}zquez Pombo.
\newblock A {{Hybrid Power System}} for a {{Permanent Colony}} on {{Mars}}.
\newblock {\em Space: Science \& Technology}, 2021, January 2021.

\bibitem{schwanbeckInternationalSpaceStation2019}
Eugene Schwanbeck and Penni Dalton.
\newblock International {{Space Station Lithium-ion Batteries}} for {{Primary
  Electric Power System}}.
\newblock In {\em 2019 {{European Space Power Conference}} ({{ESPC}})}, pages
  1--1. {IEEE}, September 2019.

\bibitem{visairoReconfigurableBatteryPack2008}
H.~Visairo and P.~Kumar.
\newblock A reconfigurable battery pack for improving power conversion
  efficiency in portable devices.
\newblock In {\em 2008 7th {{International Caribbean Conference}} on
  {{Devices}}, {{Circuits}} and {{Systems}}}, pages 1--6. {IEEE}, April 2008.

\bibitem{yangUnbalancedDischargingAging2016}
Naixing Yang, Xiongwen Zhang, BinBin Shang, and Guojun Li.
\newblock Unbalanced discharging and aging due to temperature differences among
  the cells in a lithium-ion battery pack with parallel combination.
\newblock {\em Journal of Power Sources}, 306:733--741, February 2016.

\bibitem{yangBatteryEnergyStorage2018}
Yuqing Yang, Stephen Bremner, Chris Menictas, and Merlinde Kay.
\newblock Battery energy storage system size determination in renewable energy
  systems: {{A}} review.
\newblock {\em Renewable and Sustainable Energy Reviews}, 91:109--125, August
  2018.

\bibitem{zhangDevelopmentProspectChinese2021}
Lihua Zhang.
\newblock Development and {{Prospect}} of {{Chinese Lunar Relay Communication
  Satellite}}.
\newblock {\em Space: Science \& Technology}, 2021, January 2021.

\end{thebibliography}

% \bibliographystyle{plain}
% \bibliography{sst_main}

>>>>

% 【version: SST-1.4】

% 【done】 
% =====0909
% 按 Q 修改意见修改 0901 【优先】
% =====0910
% 1. 摘要修改，量化我们的成果：explain the most important achievements of the proposed method quantitatively
% 2. 介绍修改，相关文献：
%   2.1 RBS 结构分析相关的
%   2.2 网络流（最大流）相关（但因为问题不同，无法使用，提一句穷举）
% 3. 介绍修改，逐点列出我们的贡献：state research contribution and achievements as bullet points at the end of the Introduction section
% 4. 讨论修改，增加算法复杂度，以及和穷举法的比较（该领域尚为空白，没有sota的算法）
% 5. 讨论修改，增加算法的 limitations（根据复杂度，大规模不好用）
% 6. 讨论修改，增加结果的准确性介绍（和穷举结果比较）：explain about the accuracy, sufficiency and reliability of their results? How do they verify and validate the results
% 7. 修改算法的第15步
% 8. 重写总结
% 9. 添加文献
% =====0911
% 1. introduction 整体逻辑不流畅，跳跃过大
% 2. introduction 文献
% 2. conclusion 结尾，可以加上一两句说说这个方法的应用价值之类的，吹一吹
% 3. abstract
%   3.1 删去 75000 倍的效率；
%   3.2 凝练一点，就是说这个方法把遍历法中的枚举开关状态组合，转换为了对最短路径的组合；
%   3.3 算法复杂度、效率提升倍数=2^开关数/2^电池数
%   3.4 调整 discussion 的相关内容
% 4. 删去 最大流
% 5. 按 Q 的意见修改
% =====0913
% 1. 按师兄的修改意见修改（0912晚）
% 2. 调整文献顺序，改用 biber

@@

% \usepackage[final]{changes}
\usepackage[defaultcolor=red]{changes}
% \added{xxx}
% \deleted{xxxx}
% \replaced{a}{b} 原文的b替换成a
% \usepackage{easyReview} % texstudio 部分

%%%%%% Bibliography %%%%%%
% Replace "sample" in the \addbibresource line below with the name of your .bib file.
\usepackage[style=nejm, citestyle=numeric-comp, sorting=none]{biblatex}
\addbibresource{SST_main.bib}

@@

\added{
Recently, various types of RBS with different flexibility and reconfigurability have been designed to meet application requirements. 
For example, Ci et al. \cite{ci2007novel} proposed a RBS structure that can dynamically adjust the batteries discharge rate to fully exploit the available capacity of each battery. 
Jan's \cite{9209774,engelhardt2021double} structures had the ability to reconfigure structures with variant batteries in series to reach the voltage requirements during electric vehicle charging, which constantly change.
The structure proposed by Visairo et al.\cite{visairoReconfigurableBatteryPack2008}, as shown in Figure \ref{fig:stru-Visairo}, can change the system's output voltage based on load conditions, thereby reducing the power loss of the voltage regulator during the power supply process and improving energy utilization efficiency. 
For the same purpose to enhance the energy efficiency of the system, Lawson et al. \cite{lawsonSoftwareConfigurableBattery2012} and He et al. \cite{he2014reconfiguration} also proposed simplified structures which has less switches than Visairo's design.
Kim et al. \cite{kim2009dynamic} improved the system's ability to recover from battery failures by introducing multiple ports to the structure. 
The complex structure between batteries and switches enables the flexibility of RBS, but also brings the challenges in design and control of system. 
Thus, several approaches to analyze the RBS structure and performance have been proposed in the literature to tackle these challenges.
For instance, 
Han et al.\cite{han2021analysis} derived an analytical expression for the maximum switch current during battery system reconfiguration for a specific RBS structure. 
This helps guide the selection of switches and provide support for the hardware design of RBS.
Chen et al.\cite{chenSneakCircuitTheory2021} proposed a systematic approach based on the sneak circuit theory to fundamentally avoid the short-circuit problem of reconfigurable battery systems. 
They thoroughly analyzes all paths between the cathode and anode of each battery in the RBS and identifies paths that only contain switches as short-circuit paths for pre-checking before system reconfiguration. 
}

\added{
In spite of maximum switch current mentioned above, the maximum allowable current (MAC), defined as the maximum current allowed by system under the constraints of the battery cell, is another critical indictor of RBS that need to be evaluated during the design or control process of system. 
It helps the designers to assess whether the RBS meets the output current requirements, and contribute to the formulation of appropriate and safe management strategies for the battery management system (BMS).
Unfortunately, few studies on the RBS structure analysis have been conducted to determine the MAC of RBSs.
A intuitive and straightforward method is to enumerate all possible switch states and calculate the output current of the system under each reconfigurated structure.
But this method is inefficient and time-consuming, especially for RBSs with a large number of switches.
}

@@

\added{
To solve this issue, a new method to effectively evaluate the MAC of RBS is proposed in this paper. 
First, a greedy algorithm is designed to search the possible circuit topology of RBS with MAC effciently.
Meanwhile, an improved direct graph model, considering the voltage, internal resistance, and maximum allowable current of the battery, and the external load, is porposed to obtain the accurate current value of RBS under specific circuit topology. 
To the best of our knowledge, the present work is the first to develop an efficient calculation method of RBS MAC.
}
\deleted{In this study, a directed graph model and greedy algorithm are employed to determine the MAC of RBS and the corresponding control strategy, effectively calculating the MAC for RBSs with arbitrary structures, including scenarios with isolated batteries.}
\added{The main contributions of the paper can be summarized as follows:}
\begin{itemize}
  \item \added{Proposing a effective method to determine the MAC of RBSs with arbitrary structures, including scenarios with isolated batteries.}
  \item \added{Application of the greedy algorithm to solve the MAC problem, whose computational complexity is greatly reduced compared with the brute force algorithm.}
  \item \added{introducing an improved directed graph model, considering the voltage, internal resistance, and maximum allowable current of the battery, and the external load, to achieve the current analysis of the RBS.}
\end{itemize}

@@

\added{
From the literature research we have conducted, no formal report on the algorithm for MAC in RBS has been found yet.
The brute force algorithm, which goes through all possible switch states, is the most straightforward way to solve the MAC problem and is used as a benchmark for the proposed greedy algorithm.
Assuming that a RBS has $N_b$ batteries and $N_s$ switches, and the corresponding directed graph has $N$ nodes, it requires $2^{N_s}$ iterations to traverse all reconfigured structures.
The calculation for each reconfigured structure by Equations \ref{eq:I_o}-\ref{eq:eta} requires matrix inversion and matrix multiplication, with a time complexity of $O(N^3+2N^2N_b+N^2N_s+NN^2_b)$.
Therefore, the time complexity of the brute force algorithm is $O(2^{N_s}(N^3+2N^2N_b+N^2N_s+NN^2_b))$.
The greedy algorithm proposed in this paper requires find the $SP$ for each battery, which requires $N_b$ iterations.
Each $SP$ can be obtained by couple Dijkstra algorithms.
Therefore, the total time complexity of calculating all $SP$s is $O(2N_b(N_b+2N_s)\log N)$.
According to the Appendix \ref{alg:greedy}, the RBS can reconfigure $C^{N_{set}}_{N_b}$ structures by selecting $N_{set}$ batteries from $N_b$ batteries, which is $\sum^{N_b}_{N_{set}=1}C^{N_{set}}_{N_b}/N_b \approx 2^{N_b}/N_b$ on average.
Hence, with bisection method, the time complexity of the greedy algorithm is $O(2^{N_b}/N_b(N^3+2N^2N_b+N^2N_s+NN^2_b)\log N_b+2N_b(N_b+2N_s)\log N)$, i.e., $O(2^{N_b}/N_b(N^3+2N^2N_b+N^2N_s+NN^2_b)\log N_b)$.
Based on currently proposed RBS structures\cite{ciNovelDesignAdaptive2007,alahmadBatterySwitchArray2008,kimDependableEfficientScalable2010b,kimBalancedReconfigurationStorage2011a,taesickimSeriesconnectedSelfreconfigurableMulticell2012a,6843711}, the number of batteries $N_b$, switches $N_s$, and nodes $N$ have the following quantitative relationships: $N_s \approx (3\sim 5)N_b$, $N \approx N_s$. 
After simplifying, the time complexity of the greedy algorithm is $O(2^{N_b}N_s^2\log N_b)$, while it is $O(2^{N_s}N_s^3)$ for brute force algorithm.
Therefore, it is reasonable to believe that as the size of the RBS increases, especially the number of the switches, the greedy algorithm will have an advantage over the algorithm that goes through all reconfigured structures.
This can be confirmed from the number of structures required for MAC determination in the previous subsection. 
Compared to the brute force algorithm, the efficiency of the method based on the greedy algorithm has been improved by 3000 to 75000 times, which is theoretically $N_s 2^{N_s - N_b} \log N_b$ times according to the above time complexity analysis.
Among the three RBS structures, the highest is the RBS structure with 19 switches (Figure \ref{fig:study-stru-my}).
This benefit from two key points:
(1) The $SP$s guide the RBS to reconfigure reasonable structures, rather than blindly going through all possible structures. This reduces the factor in complexity from $2^{N_s}$ to $2^{N_b}$, which is the main reason for the improvement in efficiency;
(2) The bisection method further accelerates this process.
However, the greedy algorithm proposed in this paper still contains exponential terms in the time complexity, which means it may not be able to handle extremely large-scale RBS structures.
}

@@

This paper proposes a pervasive and automatical method for computing the MAC of \replaced{a}{the} given RBS \added{efficiently}.
\added{
The method is implemented by a greedy algorithm combined with a directed graph model which considers the voltage, internal resistance, and maximum allowable current of the batteries, as well as the external load.
The main advantage of this method is its ability to calculate the MAC of RBSs with arbitrary structures.
Even in the scenarios with random isolated batteries, the method remains effective.
Compared with the brute force algorithm, the proposed method has higher computational efficiency under the same calculation results.
This is achieved by two key points when constructing the greedy algorithm: 
(1) Calculate the shortest path of each battery by Dijkstra algorithm to obtain the $SP$ of each battery; 
(2) determine the maximum number of available batteries by bisection method to reduce the computational complexity.
This method helps to fully tap the current output potential of the RBS, guide the RBS structure design and optimization in the design stage, and assist in evaluating the current overload risk of the system in practical applications.
}
\deleted{The method is implemented by a greedy algorithm combined with a directed graph model , whose effectiveness is tested on a novel and complex RBS structure.
The method remains effective for the application scenario of RBS battery isolation and demonstrates that the novel structure has the advantage on flexible output current and convenient battery isolation.
Future research could focus on developing new indictors to evaluate the performance of the RBS with the currents and voltages obtained by the method, as well as modifying the equivalent model of the battery to allow for more accurate simulations of the RBS, including transient analysis.}

@@

This work does not require any data to be declared or publicly disclosed.

% \bibliographystyle{nejm}
% \bibliography{sst_main}

\printbibliography
